---
title: "Sentiment analysis"
author: "Josephine (Aka the firebreather)"
date: "May 2, 2018"
output: html_document
---


#Welcome to the wonderful tale of the silver-scaled corrrelational dragon. We will follow the dragon as it embarks on an awesome new adventure! A sentiment analysis *insert scary music*
We don't need to set WD due to us using github


#Load in packages for our sentiment analysis.


```{r setup, include=FALSE}
library(tesseract) #This is for reading in the non-machinereadable PDFs - you need to download the danish part of it if using it yourself - code inserted below this chunk

#Run this line to get the danish stuff
danish <- tesseract("dan")
```

This is the code for getting the Danish part

**Run this** to get the danish stuff.
tesseract_download("dan")
danish <- tesseract("dan")



##Okay - the Dragon has come to a mountain.
##Aka, let us load in one article and do a sentiment analysis *Insert screaming smiley*
This mountain is an article from politiken. The dragon now tries to load in the article.


```{r}
A2 <- ocr("P_A1_fly_Y2011.pdf", engine = danish)

#Try with JP
A1 <- ocr("J_A1_fly_Y2013.pdf", engine = danish)

A3 <- ocr("b_A1_fly_Y2011.pdf", engine = danish)


write.csv(A1, "A1JP.txt")

write.csv(A2, "A1P.txt")

write.csv(A3, "A1B.txt")
```


Try with machine readable stuff

```{r}

library(tm)
library(pdftools)

text = pdf_text("p_A1_fly_Y2011.pdf")

```

